\huge Risk of non-Hodgkin lymphoma under hypothetical interventions with guaranteed positivity

### 2023-08-05 reports/SER (2023)/resources/intervention-density.tex
New intervention

% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:21
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,195.13);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[fill=fillColor] (172.93, 85.04) rectangle (184.59,125.28);

\path[fill=fillColor] (184.59, 85.04) rectangle (196.25,109.90);

\path[fill=fillColor] (196.25, 85.04) rectangle (207.90, 94.28);

\path[fill=fillColor] (207.90, 85.04) rectangle (219.56, 90.96);

\path[fill=fillColor] (219.56, 85.04) rectangle (231.21, 85.54);

\path[fill=fillColor] (231.21, 85.04) rectangle (242.87, 85.72);

\path[fill=fillColor] (242.87, 85.04) rectangle (254.52, 85.06);
\definecolor{drawColor}{RGB}{186,129,35}

@@

\path[draw=drawColor,line width= 3.2pt] (114.66, 85.04) rectangle (126.31, 88.47);

@@

\path[draw=drawColor,line width= 3.2pt] (161.28, 85.04) rectangle (172.93,124.15);

\path[draw=drawColor,line width= 3.2pt] (172.93, 85.04) rectangle (184.59,132.93);

\path[draw=drawColor,line width= 3.2pt] (184.59, 85.04) rectangle (196.25,141.93);

\path[draw=drawColor,line width= 3.2pt] (196.25, 85.04) rectangle (207.90,115.25);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,106.25) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,130.22) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,154.19) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,178.16) {0.8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,132.98) --
	( 34.23,132.98);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,156.95) --
	( 34.23,156.95);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,180.92) --
	( 34.23,180.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:02
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,195.13);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[fill=fillColor] (172.93, 85.04) rectangle (184.59,134.47);

\path[fill=fillColor] (184.59, 85.04) rectangle (196.25,107.84);

\path[fill=fillColor] (196.25, 85.04) rectangle (207.90, 91.09);

\path[fill=fillColor] (207.90, 85.04) rectangle (219.56, 87.76);

\path[fill=fillColor] (219.56, 85.04) rectangle (231.21, 85.25);

\path[fill=fillColor] (231.21, 85.04) rectangle (242.87, 85.35);

\path[fill=fillColor] (242.87, 85.04) rectangle (254.52, 85.04);
\definecolor{drawColor}{RGB}{186,129,35}

@@

\path[draw=drawColor,line width= 3.2pt] (114.66, 85.04) rectangle (126.31, 88.48);

@@

\path[draw=drawColor,line width= 3.2pt] (161.28, 85.04) rectangle (172.93,124.16);

\path[draw=drawColor,line width= 3.2pt] (172.93, 85.04) rectangle (184.59,132.94);

\path[draw=drawColor,line width= 3.2pt] (184.59, 85.04) rectangle (196.25,141.94);

\path[draw=drawColor,line width= 3.2pt] (196.25, 85.04) rectangle (207.90,115.26);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,106.26) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,130.23) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,154.21) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,178.18) {0.8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,132.99) --
	( 34.23,132.99);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,156.96) --
	( 34.23,156.96);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,180.94) --
	( 34.23,180.94);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}
